preprocessing

### 2022-10-24 r-analysis/analysis.Rmd
added EU to PerCapAnalysis

```{r overview statistics: emissions per capita development 1970:2020}
YEAR = 2019

source("r-analysis/china_and_regions.R", local = TRUE, print.eval = TRUE)
source("r-plots/china_and_regions.R", local = TRUE, print.eval = TRUE)

@@

```{r overview statistics: emissions by sector development 1970:2020 }
data_countries <- data_ghg %>% 
  group_by(ISO,country,year,sector) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE))

>>>>

```{r overview statistics: emissions per capita }
YEAR = 2019
COUNTRY= "China"    
source("r-analysis/per_capita_emissions_china_and_regions", local = TRUE, print.eval = TRUE)
source("r-plots/plot_bar_per_capita_emissions_2019", local = TRUE, print.eval = TRUE)

@@

```{r overview statistics: emissions by sector }
data_countries <- data_base %>% 
  group_by(ISO,country,year,sector_title) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE))

#plot

```{r overview statistics: absolute emissions by gas}
data_countries <- data_base %>% 
  group_by(ISO,country,year,sector_title) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE))

#plot

### 2022-10-24 r-prep/prep.Rmd
added EU to PerCapAnalysis

data_base = data_gwp100 %>%
  left_join(data_wdi,by=c("ISO","year")) %>%
  mutate(GHG_pc = GHG/pop) %>%
  mutate(GDP_pc = gdp_ppp/pop)

>>>>

data_base = data_gwp100 %>%
  left_join(data_wdi,by=c("ISO","year")) %>%
  mutate(GHG_pc = GHG/pop) %>%
  mutate(GDP_pc = gdp_ppp/pop) %>%
  filter(year <= 2019) %>% 
  mutate(EU= case_when(country %cin% eurostat::eu_countries[2]~ TRUE))
